---
title: "Ongoing Reporting of the Data Collection "
author: "Julie Faure-Lacroix (Calcul Québec), Eugene Low (NSCC Singapore), Suzanne Talon (Calcul Québec)"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(tm)
library(tidytext)
library(wordcloud)
library(tidyverse)
data2026 <- read.csv("./fake_hpc_events.csv")
data2026$year <- year(data2026$date)
```

## Context
This is where the context goes. 


## History of the surveys

We started polling the community during SCA-HPCA 2026 in Osaka Japan. 
```{r echo = FALSE, message=FALSE}
# number of submitted responses per event per year
groups <- group_by(data2026,year,event)
kable(summarise(groups,max(user)), col.names = c("Year", "Event", "Number of Participants"))
```


## Stability of funding over the years

Countries have seen changes in the stability of funding.

```{r echo=FALSE}
ggplot(data = data2026, aes(x = factor(year), y = user, fill = factor(funding_guaranteed))) +
  geom_col(position = "dodge") +
  labs(x = "Year", y = "Numbers of votes", fill = "Is Funding Guaranteed")
```

## Metrics Currently Most Relevant 

Here are the most commonly used metrics when reporting to funding agencies.

```{r echo=FALSE, message = FALSE, warning=FALSE}
# word cloud example
metricstext <- data2026$top_three_metrics
corpuswords <- Corpus(VectorSource(metricstext))
tdmx <- TermDocumentMatrix(corpuswords)
wordmatrix <- as.matrix(tdmx) 
wordcount <- sort(rowSums(wordmatrix),decreasing=TRUE) 
wordfrequency <- data.frame(word = names(wordcount),freq=wordcount)
metric_words <-  data2026 %>%
  select(top_three_metrics) %>%
  mutate(top_three_metrics = str_replace_all(top_three_metrics, "-", "_")) %>% # tidytext strips - but not _, so that's a workaround
  unnest_tokens(word, top_three_metrics)
words <- metric_words %>% count(word, sort=TRUE)
set.seed(1234) # for reproducibility
wordcloud(words = wordfrequency$word, freq = wordfrequency$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35,
          colors=brewer.pal(8, "Dark2"))
```

## Evolution of Metric Trends Over the Years
```{r echo=FALSE, message = FALSE, warning=FALSE}
ggplot(data = data2026, aes(x = factor(year), y = user, fill = factor(funding_guaranteed))) +
  geom_col(position = "dodge") +
  labs(x = "Year", y = "Numbers of votes", fill = "Is Funding Guaranteed")
```